Finiteness in Cubical Type Theory

### 2020-06-12 paper.tex
rearranged more
cleaner format
countdown
switched to acmart
more introduction
Update paper.tex

\author{
  Donnacha Oisín Kidney \and
  Gregory Provan \and
  Nicolas Wu
}
% \affiliation{University College Cork}
% \email{o.kidney@cs.ucc.ie}
% \author{Gregory Provan}
% \affiliation{University College Cork}
% \email{g.provan@cs.ucc.ie}
% \author{Nicolas Wu}
% \affiliation{Imperial College London}
% \email{n.wu@imperial.ac.uk}

@@

% \keywords{Agda, Homotopy Type Theory, Cubical Type Theory,
%   Dependent Types, Finiteness, Topos, Kuratowski finite}

\maketitle
% \begin{abstract}
%   We study five different notions of finiteness in Cubical Type Theory and prove
%   the relationship between them.
%   In particular we show that any totally ordered Kuratowski finite type is
%   manifestly Bishop finite.

%   We also prove closure properties for each finite type, and classify them
%   topos-theoretically.
%   This includes a proof that the category of decidable Kuratowski finite sets
%   (also called the category of cardinal finite sets) form a \(\Pi\)-pretopos.

%   We then develop a parallel classification for the countably infinite types, as
%   well as a proof of the countability of \(A^\star\) for a countable type \(A\).

%   We formalise our work in Cubical Agda, where we implement a library for proof
%   search (including combinators for level-polymorphic fully generic currying).
%   Through this library we demonstrate a number of uses for the computational
%   content of the univalence axiom, including searching for and synthesising
%   functions.
% \end{abstract}
\include{sections/introduction}
\include{sections/finiteness-predicates}
\include{sections/topos}
\include{sections/countable-predicates}
\include{sections/search}
\include{sections/related-work}

% \begin{acks}
%   This work has been supported by the Science Foundation Ireland under the
%   following grant: 13/RC/2D94 to Irish Software Research Centre.
% \end{acks}

\bibliographystyle{plain}
\bibliography{bibliography}
\end{document}

>>>>

@@

\author{Donnacha Oisín Kidney}
\author{Gregory Provan}
\author{Nicolas Wu}

\begin{abstract}
  We study five different notions of finiteness in Cubical Type Theory and prove
  the relationship between them.
  In particular we show that any totally ordered Kuratowski finite type is
  manifestly Bishop finite.

  We also prove closure properties for each finite type, and classify them
  topos-theoretically.
  This includes a proof that the category of decidable Kuratowski finite sets
  (also called the category of cardinal finite sets) form a \(\Pi\)-pretopos.

  We then develop a parallel classification for the countably infinite types, as
  well as a proof of the countability of \(A^\star\) for a countable type \(A\).

  We formalise our work in Cubical Agda, where we implement a library for proof
  search (including combinators for level-polymorphic fully generic currying).
  Through this library we demonstrate a number of uses for the computational
  content of the univalence axiom, including searching for and synthesising
  functions.
\end{abstract}

\keywords{Agda, Homotopy Type Theory, Cubical Type Theory,
  Dependent Types, Finiteness, Topos, Kuratowski finite}

\maketitle

\include{sections/introduction}
\include{sections/finiteness-predicates}
\include{sections/topos}
\include{sections/countable-predicates}
\include{sections/search}
\include{sections/countdown}
\include{sections/related-work}

% \begin{acks}
%   This work has been supported by the Science Foundation Ireland under the
%   following grant: 13/RC/2D94 to Irish Software Research Centre.
% \end{acks}
\bibliography{bibliography}
\end{document}
